Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-03 WSSSPE2_report/WSSSPE2_review.tex
rewording a little of new entry, and setting line endings back to Unix style

Venters proposed that technically sustainable software is a composite, first-class, non-functional requirement (NFR) 
that is at a minimum a measure of a systems maintainability and extensibility but may also include other NFR such as 
efficiency (energy and cost), interoperability, portability, reusability, scalability, and usability. To achieve 
technically sustainable software it was suggested that software architectures are fundamental as they are the primary 
carrier of system qualities (NFR) i.e. pre-system understanding, and influence how developers are able to understand, 
analyze, extend, test and maintain a software system i.e. post-deployment system understanding. In addition, it was 
highligted that the sustainability of software architectures also needs to be addressed to endure different types of 
change and evolution in order to mitigate architectural drift and erosion, and architectural knowledge vaporization.

>>>>

Venters proposed that technically sustainable software is a composite, first-class, 
non-functional requirement (NFR) that is at a minimum a measure of a systems 
maintainability and extensibility but may also include other NFR such as efficiency 
(energy and cost), interoperability, portability, reusability, scalability, and usability. To 
achieve technically sustainable software Venters suggested that software 
architectures are fundamental as they are the primary carrier of system qualities 
(NFR), i.e., pre-system understanding, and influence how developers are able to 
understand, analyze, extend, test and maintain a software system, i.e., post-
deployment system understanding. In addition, Venters highlighted that the 
sustainability of software architectures also needs to be addressed to endure 
different types of change and evolution in order to mitigate architectural drift and 
erosion, and architectural knowledge vaporization.
